Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
removed the quantum causal model and changed the labels on the large inequalities from sec: to eq:

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}). \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions. Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements on the quantum causal model depicted in \cref{fig:triangle_structure_quantum_model}. The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
    While the states shared with $C$ are the following mixed states:
    \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
    The measurements employed by $A,B$ and $C$ are separable, projective measurements,
    \begin{align*}
        M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
        M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{align*}
    Where $\ket{\psi_n}$ is shorthand for,
    \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
    Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.

@@

    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution. The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_web}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires. Using this incidence matrix, a number of incompatibility certificates were derived. For inspection, one is reproduced in \cref{sec:web_inequality}.

    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems. Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent. Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}). Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}. This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{sec:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality. In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.

    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{sec:web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{sec:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033) \]

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities. In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}). Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible. We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.  Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.

@@

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e. $U \ket{\psi_j} = \ket{j}$. First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$. Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}. This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}. Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$. Since $\Tr\bc{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}. Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$. For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant in \cref{eq:quantum_model_triangle_pvms}.
    \[  \]
    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}. Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.

@@

@@

    % \subsection{Parameterizing Quantum Distributions}
    \begin{figure}
    \begin{center}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
            \caption{The Triangle structure as modeled by quantum states and measurements.}
            \label{fig:triangle_structure_quantum_model}
    \end{center}
    \end{figure}

    % \subsection{Numerical Optimization Results}
    \label{sec:results}

    For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]

>>>>

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities. A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{eq:web_inequality,eq:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}). \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work. Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}. \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions. Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements. The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
    While the states shared with $C$ are the following mixed states:
    \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
    The measurements employed by $A,B$ and $C$ are separable, projective measurements,
    \begin{align*}
        M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
        M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{align*}
    Where $\ket{\psi_n}$ is shorthand for,
    \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
    Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.

@@

    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution. The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_web}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires. Using this incidence matrix, a number of incompatibility certificates were derived. For inspection, one is reproduced in \cref{eq:web_inequality}.

    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems. Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent. Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}). Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}. This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{eq:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality. In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.

    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{eq:web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{eq:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033) \]

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities. In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}). Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible. We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.  Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.

@@

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e. $U \ket{\psi_j} = \ket{j}$. First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$. Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}. This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}. Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$. Since $\Tr\bc{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}. Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$. For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant for \cref{eq:quantum_model_triangle_pvms}.

    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}. Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.

@@

    % \subsection{Parameterizing Quantum Distributions}
    % \begin{figure}
    % \begin{center}
    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
    %         \label{fig:triangle_structure_quantum_model}
    % \end{center}
    % \end{figure}

    % \subsection{Numerical Optimization Results}

    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e. $V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$. The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}. At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution. In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events. What does this reveal about $I_1$ and non-classicality in the Triangle structure? This result is not entirely unexpected. As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the Triangle structure. Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.

    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
            \label{fig:maximum_violation_I_1}
    \end{center}
    \end{figure}

@@
